---
title: "MATH 216 Homework 4"
author: "Connor"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    smooth_scroll: false
---

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4.5}
# Suggested packages; feel free to use more!
library(tidyverse)
library(USAboundaries)
library(maptools)
library(sp)
library(broom)
library(ggthemes)
library(broom)
library(ggplot2)
```



## Admistrative:

Please indicate

* Who you collaborated with: Trisha
* Roughly how much time you spent on this HW so far: 5
* The URL of the RPubs published URL [here](http://rpubs.com/connormccormick/hw4).
* What gave you the most trouble: Calculating the distances because I did not check the website for hints and thought we had to calculate spherical distances. 
* Any comments you have: How can I shiny app to the bounds of the US besides using the extremes of the coordinates?



## Question 1:

**Question**:  DHL, a German shipping company, has a ton of money to build a
shipping hub in the United States. Where should they build it?

**Deliverable**: A choropleth map of the lower 48 states (no Puerto Rico) where
the color corresponds to the distance of the given area to the shipping hub,
which is marked on the map with a large red dot.

```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4.5}
# Perform your computations here:
counties_shp <- us_counties() 
centroids <- coordinates(counties_shp)
counties_data <- counties_shp@data %>%
  mutate(centroidlong = coordinates(counties_shp)[,1]) %>%
  mutate(centroidlat = coordinates(counties_shp)[,2]) 
counties_polygon <- tidy(counties_shp, region="geoid")
counties <- left_join(counties_polygon, counties_data, by=c("id"="geoid"))


counties <- counties %>%
  filter( !state_name %in% c("Alaska", "Hawaii", "Puerto Rico"))

countydistances <- counties %>%
  mutate(dist = (sqrt((centroidlong+85)^2 + (centroidlat-33)^2)))





```


```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4.5}
# Here is a template of a ggplot call; feel free to change this to suit your
# needs. Once your computations above are complete, set the eval=TRUE on the
# line above to tell R Markdown to run this code block.

ggplot(countydistances, aes(x=long, y=lat, group = group, fill = dist)) +
  geom_polygon() +
  geom_path(color = "darkslateblue", size = .1)+
  scale_fill_gradient(low="white", high="darkgreen") + 
  annotate("point", x=(-85), y=33, col="violetred2", size=3) +
  coord_map()


```

I made a shiny app



