---
title: "MATH 216 Homework 4"
author: "Connor"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    smooth_scroll: false
---

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4.5}
# Suggested packages; feel free to use more!
library(tidyverse)
library(USAboundaries)
library(maptools)
library(sp)
library(broom)
library(ggthemes)
library(broom)
library(ggplot2)
```



## Admistrative:

Please indicate

* Who you collaborated with: Trisha
* Roughly how much time you spent on this HW so far: 8
* The URL of the RPubs published URL [here](http://rpubs.com/connormccormick/hw4).
* What gave you the most trouble: 
* Any comments you have: Could not figure out how to calculate the centroid of population



## Question 1:

**Question**:  DHL, a German shipping company, has a ton of money to build a
shipping hub in the United States. Where should they build it?

**Deliverable**: A choropleth map of the lower 48 states (no Puerto Rico) where
the color corresponds to the distance of the given area to the shipping hub,
which is marked on the map with a large red dot.

```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4.5}
# Perform your computations here:
Census2010 <- read_csv("~/Documents/Middlebury/Data Science/HW4/Census2010.csv") %>%
  select_("Geo_FIPS", "SE_T001_001")
counties_shp <- us_counties() 
centroids <- coordinates(counties_shp)
counties_data <- counties_shp@data %>%
  mutate(centroidlong = coordinates(counties_shp)[,1]) %>%
  mutate(centroidlat = coordinates(counties_shp)[,2]) 
counties_polygon <- tidy(counties_shp, region="geoid")
counties <- left_join(counties_polygon, counties_data, by=c("id"="geoid")) %>%
  transform(as.character("id"))
countiescensus <- left_join(counties, Census2010, by=c("id" = "Geo_FIPS"))


countiesnew <- countiescensus %>%
  filter( !state_name %in% c("Alaska", "Hawaii", "Puerto Rico")) %>%
  mutate(waitcentroidlong = SE_T001_001*centroidlong) %>%
  mutate(waitcentroidlat = SE_T001_001*centroidlat) 

#latitude
# countiesweighted <- countiesnew %>%
#     sum(as.numeric(countiesnew$waitcentroidlat))/sum(as.numeric(countiesnew$SE_T001_001))
#Longitude
#   countiesweighted <- countiesnew %>%
#     filter(!(is.na(SE_T001_001))) %>%
#     filter(!(is.na(waitcentroidlong))) %>%
#     filter(!(is.na(centroidlong)))
#     sum(countiesweighted$waitcentroidlong)/sum(countiesweighted$SE_T001_001)

  
  
countydistances <- countiesnew %>%
  mutate(dist = (sqrt((centroidlong+92.173096)^2 + (centroidlat-37.517534)^2)))


countydistances <- countydistances %>%
  mutate(popdist = SE_T001_001/dist)


```


```{r, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=4.5}

ggplot(countydistances, aes(x=long, y=lat, group = group, fill = dist)) +
  geom_polygon() +
  geom_path(color = "darkslateblue", size = .1)+
  scale_fill_gradient(low="white", high="darkgreen") + 
  annotate("point", x=(-92.173096), y=37.517534, col="violetred2", size=3) +
  coord_map()

ggplot(countydistances, aes(x=long, y=lat, group = group, fill = popdist)) +
  geom_polygon() +
  geom_path(color = "darkslateblue", size = .1)+
  scale_fill_gradient(low="white", high="darkgreen") + 
  annotate("point", x=(-92.173096), y=37.517534, col="violetred2", size=3) +
  coord_map()


```
The second map takes the population of the county divided by the distance in degrees of longitude/latitude to calculate the closest heavily populated areas.

I made a shiny app



